---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

Load in the necessary files

```{r}
library(quantmod)
library(BatchGetSymbols)
library(plyr)
library(dplyr)
library(scales)
library(lubridate)
library(stringr)
library(openxlsx)
library(rvest)
#library("here")
#set_here()

getPrices <- function(x){
  tryCatch({
    prices <- as.data.frame(Cl(x))
    prices$date <- as.Date(rownames(prices))
    #print('here')
    #prices$ticker <- factor('SPY') # Need ticker symbol
    #print('h2')
    colnames(prices)[1] <- 'close'
    #print('h3')
    rownames(prices) <- NULL
    #print('Not here')
    prices$date <- ymd(prices$date)
    return(prices)
  }, error = function(err) {print(x)})
}

compareStocks <- function(tickers,timespan=4) {
  first.date <- Sys.Date() - timespan*30
  last.date <- Sys.Date()
  l.out <- BatchGetSymbols(tickers = tickers,
    first.date = first.date,
    last.date = last.date,
    cache.folder = file.path(tempdir(),
    'BGS_Cache') ) # cache in tempdir()
  allPrices <- l.out$df.tickers
  allPrices <- select(allPrices,ticker,close=price.close,date=ref.date)
  
  # Find Start price and append to rows
  iPrice <- allPrices[allPrices$date==min(allPrices$date),]
  iPrice <- subset(iPrice, select = -date)
  colnames(iPrice) <- c('ticker','startPrice')
  allPrices <- join(allPrices,iPrice)  
  
  # Scale the price by start price
  # allPrices$newPrice <- (allPrices$close/allPrices$startPrice) - 1
  allPrices$gain <- (allPrices$close/allPrices$startPrice) - 1
  allPrices$gainP <- percent((allPrices$close/allPrices$startPrice) - 1)
  
  results <- subset(allPrices,date==max(allPrices$date),select=c(date,ticker,gain,gainP))
}

compareStocksOLD <- function(tickers,timespan=4) {
  # calculate start 1 year from today
  #sDate <- today() - years(1)
  sDate <- today("GMT") - months(timespan)
  getSymbols(tickers,src='yahoo',from=as.character(sDate))
  data <- mget(tickers)
  allPrices <- ldply(data,getPrices)
  colnames(allPrices) <- c('ticker','close','date')
  #print(head(allPrices))
  
  # Find Start price and append to rows
  iPrice <- allPrices[allPrices$date==min(allPrices$date),]
  iPrice <- subset(iPrice, select = -date)
  colnames(iPrice) <- c('ticker','startPrice')
  allPrices <- join(allPrices,iPrice)  
  
  # Scale the price by start price
  # allPrices$newPrice <- (allPrices$close/allPrices$startPrice) - 1
  allPrices$gain <- (allPrices$close/allPrices$startPrice) - 1
  allPrices$gainP <- percent((allPrices$close/allPrices$startPrice) - 1)
  
  # In order to pick which one to sell
  #last <- max(ymd(allPrices$date[!is.na(allPrices$date)]))
  #first <- min(ymd(allPrices$date[!is.na(allPrices$date)]))
  #m3 <- last - days(90)
  #m6 <- last - days(180)
  # Create df with tickers and purchase date
  # Calculate gain for past year
  # subset(allPrices,date==last | date==m6 | date==m3,select=c(date,ticker,gain))
  results <- subset(allPrices,date==max(allPrices$date),select=c(date,ticker,gain,gainP))
  # Sort results by gain descending
  #print(results[order(-results$gain),c('ticker','gainP')])
}

# update!  run bash shell, load xlsx, convert
# Update data files
fd <- file.info("ss.xlsx")$mtime
cd <- Sys.time()
dt <- difftime(cd, fd, units = "hours")
if (dt > 10) {
  #system("./getSS.sh")
  #system("./getET.sh")
}

callmorningstar <- function(ticker) {
  url <- paste("http://financials.morningstar.com/company-profile/c.action?t=",
                ticker,"&region=usa&culture=en-US",sep="")

  writeLines(sprintf("var page = require('webpage').create();
  page.open('%s', function () {
      console.log(page.content); //page source
      phantom.exit();
  });", url), con="scrape.js")
  
  system("phantomjs scrape.js > scrape.html")
  
  # extract the content you need
  pg <- read_html("scrape.html")
  nt <- html_nodes(pg, xpath='//td') %>% html_text()
  stockType <- nt[1]
  stockSector <- nt[32]
  stockIndustry <- nt[34]
  data.frame(ticker=ticker,type=stockType,sector=stockSector,industry=stockIndustry)
}


```

Read the files and prepare for processing
```{r}
et <- read.csv('etrade.csv',stringsAsFactors = FALSE,skip=10) 
#et <- filter(et,!(Symbol %in% c('CASH','TOTAL')))
et <- head(et,-3)
portfolio <- mutate(et,type=ifelse(Symbol %in% c('YAFFX','PENNX','HFCGX','FAGIX','CHTTX','RZV','DGS','FM','VNQ','FPX','SPY','WHOSX','RSP','EQAL'),'fund','stock'))
#h2 <- read.csv("pfmDownload.csv",stringsAsFactors=FALSE)
colnames(portfolio) <- gsub("[^[:alnum:]///' ]", "", colnames(portfolio))
h2 <- filter(portfolio,type=='stock')
h2$Ticker <- as.character(h2$Symbol)
holdings <- h2$Ticker
holdings <- c(holdings,'CHGG','SPY')



p <- read.xlsx('ss.xlsx',1,skipEmptyRows = TRUE)
#p <- rename(p,Ticker=Company.(Ticker))
#colnames(p)[1] <- "Ticker"
#p <- mutate(p,Ticker=str_extract(Ticker,'\\(.+\\)'))
#p <- filter(p,!is.na(Ticker))
#p$Ticker <- str_replace_all(p$Ticker,'[\\(\\)]','')
#p <- read.csv('shadow_stock_portfolio.csv',skip=2,stringsAsFactors=FALSE)
#p2 <- read.csv("results.csv")
p2 <- filter(p,!(Ticker %in% holdings))
#p2 <- filter(p2,Score > 1,!(Ticker %in% holdings))
p2$Ticker <- as.character(p2$Ticker)
prospects <- p2$Ticker
prospects <- c(prospects,'SPY')

candidates <- filter(h2,!(Ticker %in% prospects))

```



The window we're looking at is 4 months.

Collecting Holdings
```{r}
todrop <- compareStocks(holdings)
todrop %>% arrange(-gain) %>% select(ticker,gainP)
```


Collecting Prospects
```{r}
prospects <- prospects[prospects != 'GLPW']
picks <- compareStocks(prospects)
picks %>% arrange(-gain) %>% select(ticker,gainP)
```
Shadow Stock Notes - shows new stocks and probationary stocks.
```{r}
#filter(h2,!(Ticker %in% p$Ticker))
names(p2) <- gsub("\\.", "dot", names(p2))
#p2 <- mutate(p2, notes = NA2)
#notes <- filter(p2,str_length(NAdot)>5) %>% mutate(Notes = NAdot) %>% 
#notes <- select(p2,Ticker,Notes) %>% filter(!is.na(Notes))
#notes
```
These stocks are not in the Shadow Stock Portfolio and I should consider selling.
```{r}
# Color code compared to SPY for same periods
# Go back to original financial package and see how much of this it can do

# Plot performance over past year
#ggplot(allPrices,aes(x=date,y=close)) + 
#  geom_line() + scale_y_log10() + facet_wrap(~ ticker)

# Try plotting all 10 on same chart
#ggplot(allPrices,aes(x=date,y=close,colour=ticker)) +
#  geom_line() + scale_y_log10()

# plot the log price - better but not easily comparable
#ggplot(allPrices,aes(x=date,y=newPrice,colour=ticker)) + geom_line() + scale_y_log10()

aaiiSell <- filter(todrop,!(ticker %in% p$Ticker)) %>% arrange(-gain)

aaiiSell
```



Keep track of the split between stocks and funds - should be roughly 50/50
```{r}
ftotal <- sum(portfolio$Value)
groupsummary <- portfolio %>% group_by(type) %>% tally(Value) %>% mutate(share = n/ftotal)
groupsummary
```
Now lets analyze my mutual funds and their 12-month performance

```{r}
mfdesc <- read.csv('mfdesc.csv')
funds <- filter(portfolio,type=="fund")
funds <- inner_join(funds,mfdesc)
mfperf <- compareStocks(funds$Symbol,12)
mfresults <- inner_join(funds,mfperf,by=c("Symbol" = "ticker")) %>% 
  arrange(-gain) %>%  
  select(Symbol,gainP,Value,Desc,Category)
mfresults
```
New Goal
20.00%	S&P (RSP, SPY, FPX)
20.00%	MidCap (EQAL,CHTTX)
15.00%	International (FM)
15.00%	Bonds (WHOSX,FAGIX)
10.00%  SmallCap (RZV)
10.00%	Growth (HFCGX)
10.00%	REIT (VNQ)


S&P - 25%
Value - 25%
MidCap - 25%
Growth - 10%
REIT - 10%
International - 2.5%
Bonds - 2.5%

Add midcap (25K) - eqal
Add bonds (25K) - fagix

Add this calculation into the results table!
```{r}

goals <- data.frame(Category = c("S&P","MidCap","International","Bonds","SmallCap","Growth","REIT"),
                    Goal = c(.2,.2,.15,.15,.1,.1,.1))

ftotal <- groupsummary$n[groupsummary$type=='fund']
#dist <- mfresults %>% group_by(Category) %>% tally(Value) %>% mutate(share = n/ftotal) %>% arrange(-share)
dist <- funds %>% group_by(Category) %>% tally(Value) %>% mutate(share = n/ftotal)
dist <- join(dist,goals) %>% mutate(Dif = n - Goal*ftotal) %>% arrange(Dif)
dist
```

To Do:
  Download other AAII screens - add to prospects

Try to scrape from Morningstar  
```{r}
#http://www.morningstar.com/stocks/XNAS/MSFT/quote.html
#http://financials.morningstar.com/company-profile/c.action?t=MSFT&region=usa&culture=en-US


# render HTML from the site with phantomjs

url <- "http://financials.morningstar.com/company-profile/c.action?t=MSFT&region=usa&culture=en-US"

writeLines(sprintf("var page = require('webpage').create();
page.open('%s', function () {
    console.log(page.content); //page source
    phantom.exit();
});", url), con="scrape.js")

system("phantomjs scrape.js > scrape.html")

# extract the content you need
pg <- read_html("scrape.html")
nt <- html_nodes(pg, xpath='//td') %>% html_text()
stockType <- nt[1]
stockSector <- nt[32]
stockIndustry <- nt[34]

```

```{r}

#read mstar file
mstar <- read.csv('mstar.csv') %>% select(-X)
#anti join
tocall <- anti_join(picks,mstar)
#ldply the rest
df <- ldply(tocall$ticker,callmorningstar)

#union with mstar
mstar <- rbind(df,mstar)

#write mstar back out
write.csv(mstar,'mstar.csv')

#callmorningstar('chgg')
#df <- ldply(prospects,callmorningstar)

```

Currently trying to pick non-Cyclical stocks, as I am over-weighted there.
```{r}

finalpicks <- join(picks,mstar) %>% arrange(-gain)
#finalpicks <- join(picks,mstar) %>% filter(type == 'Cyclical') %>% arrange(-gain)
#finalpicks <- join(picks,mstar) %>% filter(type != 'Cyclical') %>% arrange(-gain)
finalpicks
```
```{r}
tocall <- anti_join(todrop,mstar)
df <- ldply(tocall$ticker,callmorningstar)

mstar <- rbind(df,mstar)
write.csv(mstar,'mstar.csv')


finaldrops <- join(todrop,mstar) %>% arrange(-gain)
finaldrops
```

